### 2021-04-22 paper/ase21/abstract.tex
[ASE21] Updated numbers
Reflected comments

  To alleviate the problem, we propose $\tool$, a JavaScript Specification Type
  Analyzer using Refinement.  It is the first tool that performs \textit{type
  analysis} on JavaScript specifications and detects specification bugs using a
  \textit{bug detector}.  For a given specification, $\tool$ first compiles each
  abstract algorithm written in a structured natural language to a corresponding
  function in $\ires$, an untyped intermediate representation for ECMAScript.
  Then, it performs type analysis for compiled functions with specification
  types defined in ECMAScript.  Based on the result of type analysis, $\tool$
  detects specification bugs using a bug detector consisting of four checkers.
  To increase the precision of the type analysis, we present
  \textit{condition-based refinement} for type analysis, which prunes out
  infeasible abstract states using conditions of assertions and branches.  We
  evaluated $\tool$ with all 864 versions in the official ECMAScript repository
  for the recent three years from 2018 to 2021.  $\tool$ took \inred{137.3}
  seconds on average to perform type analysis for each version, and detected
  \inred{161} type-related specification bugs with \inred{56.5}\% precision;
  \inred{91} out of \inred{161} bugs are true bugs.  Among them, \inred{14}
  bugs are newly detected by $\tool$, and the committee confirmed them all.
\end{abstract}

>>>>

  To alleviate the problem, we propose $\tool$, a JavaScript Specification Type
  Analyzer using Refinement.  It is the first tool that performs \textit{type
  analysis} on JavaScript specifications and detects specification bugs using a
  \textit{bug detector}.  For a given specification, $\tool$ first compiles each
  abstract algorithm written in a structured natural language to a corresponding
  function in $\ires$, an untyped intermediate representation for ECMAScript.
  Then, it performs type analysis for compiled functions with specification
  types defined in ECMAScript.  Based on the result of type analysis, $\tool$
  detects specification bugs using a bug detector consisting of four checkers.
  To increase the precision of the type analysis, we present
  \textit{condition-based refinement} for type analysis, which prunes out
  infeasible abstract states using conditions of assertions and branches.  We
  evaluated $\tool$ with all 864 versions in the official ECMAScript repository
  for the recent three years from 2018 to 2021.  $\tool$ took 137.3
  seconds on average to perform type analysis for each version, and detected
  157 type-related specification bugs with 59.2\% precision;
  93 out of 157 bugs are true bugs.  Among them, 14
  bugs are newly detected by $\tool$, and the committee confirmed them all.
\end{abstract}

### 2021-04-22 paper/ase21/analyzer.tex
Reflected comments

We design a type analysis for the modified $\ires$ based on the abstract
interpretation framework~\cite{ai1977, ai1992} with analysis
sensitivity~\cite{sens-toplas}.  We first extend types as follows:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{0.8\columnwidth}{!}{$
    \tyset \ni \ty ::=
    \cdots \mid
    \func \mid
    \const \mid
    \bool \mid
    \str \mid
    \tabsent \mid
    \tnormal(\ty) \mid
    \tabrupt
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
We add types for functions $\func$ and constants $\const$,
\jscode{Boolean} values $\bool$ and \jscode{String} values $\str$ to precisely
handle the control flows of branches and field accesses, respectively,
the absent type $\tabsent$ to represent the absence of variables, and
$\tnormal(\ty)$ for normal completions whose \code{Value} fields have
type $\ty$ and $\tabrupt$ for abrupt completions to enhance the
analysis precision.

>>>>

We design a type analysis for the modified $\ires$ based on the abstract
interpretation framework~\cite{ai1977, ai1992} with analysis
sensitivity~\cite{sens-toplas}.  We extend types as follows:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{0.8\columnwidth}{!}{$
    \tyset \ni \ty ::=
    \cdots \mid
    \func \mid
    \const \mid
    \tabsent \mid
    \bool \mid
    \str \mid
    \tnormal(\ty) \mid
    \tabrupt
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
with function types $\func$, constant types $\const$, and
the absent type $\tabsent$ representing the absence of variables.
\jscode{Boolean} values $\bool$, \jscode{String} values $\str$,
$\tnormal(\ty)$ denoting normal completions with \code{Value} fields of type $\ty$,
and $\tabrupt$ denoting abrupt completions serve to improve the analysis precision.

### 2021-04-22 paper/ase21/checker.tex
Reflected comments

      \aseme{\uop \; \expr}(\aenv) &=& \left\{
        \begin{array}{ll}
          \text{ill-typed operand} \; \expr\ \ \,
          & \text{if} \; \asemr{\expr}(\aenv) \norder \aty\\
          \cdots
          & \text{otherwise}\\
        \end{array}
      \right.\\
    \end{array}
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
where $\aty_0$, $\aty_1$, and $\aty$ are expected abstract types of $\expr_0$,
$\expr_1$, and $\expr$, respectively.  The additional checks report
when a given operand does not conform to its expected type.  According to our
manual investigation, there existed two different kinds of ill-typed operand
bugs: two non-numeric operand bugs (\stextsf{NoNumber}) in one pull request, and
six unchecked abrupt completion bugs (\stextsf{Abrupt}) in five pull requests.

For an example of non-numeric operand bugs, consider the built-in
algorithm $\code{Math.round}$ in Figure~\ref{fig:example}(d).  The types of $\x$
and $\n$ are $\{ \tjs \}$ and $\{ \tnum \}$, respectively, because the
\textbf{ToNumber} algorithm always returns number values or abrupt completions,
and the prefix \textbf{?} removes the latter case.  The built-in algorithm
misuses $\x$ rather than $\n$ on lines 3 and 4, and because the expected
abstract type $\{ \tnum, \tbigint \}$ does not subsume $\{ \tjs \}$, the operand
checker reports non-numeric operand bugs.

An unchecked abrupt completion bug occurs when the actual value is necessary but
it is an abrupt completion.  ECMAScript has a special implicit conversion for
normal completions when their actual values stored in the $\code{Value}$ field
are necessary, such as conditions, values of field updates, and operands of
operators.  For example, if the variable $\x$ has a normal completion with
\code{42} as its actual value, $\code{x + 1}$ should be \code{43} because the
normal completion gets implicitly converted into its actual value \code{42}.  To
explicitly represent this conversion, we define a unary operator $\escaped$ as
follows:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{\columnwidth}{!}{$
    \escaped \val = \left\{
      \begin{array}{ll}
        \val &
        \text{if} \; \val \; \text{is not a completion}\\

@@

        \text{unchecked abrupt completion} \; \val &
        \text{otherwise}\\
      \end{array}
    \right.
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
and assume that the operator $\escaped$ is used when the actual value is necessary.

>>>>

      \aseme{\uop \; \expr}(\aenv) &=& \left\{
        \begin{array}{ll}
          \text{ill-typed operand} \; \expr\ \ \,
          & \text{if} \; \asemr{\expr}(\aenv) \norder \aty\\
          \cdots
          & \text{otherwise}\\
        \end{array}
      \right.\\
    \end{array}
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
where $\aty_0$, $\aty_1$, and $\aty$ are expected abstract types of $\expr_0$,
$\expr_1$, and $\expr$, respectively.  The additional checks report
when a given operand does not conform to its expected type.
Our manual investigation found two non-numeric operand bugs (\stextsf{NoNumber})
in one pull request and six unchecked abrupt completion bugs (\stextsf{Abrupt})
in five pull requests.

For an example non-numeric operand bug, consider the built-in
algorithm $\code{Math.round}$ in Figure~\ref{fig:example}(d).  The types of $\x$
and $\n$ are $\{ \tjs \}$ and $\{ \tnum \}$, respectively, because
\textbf{ToNumber} always returns number values or abrupt completions,
and the prefix \textbf{?} removes the latter case.  The built-in algorithm
misuses $\x$ rather than $\n$ on lines 3 and 4, and because the expected
abstract type $\{ \tnum, \tbigint \}$ does not subsume $\{ \tjs \}$, the operand
checker reports non-numeric operand bugs.

An unchecked abrupt completion bug occurs when an actual value is necessary but
it is an abrupt completion.  ECMAScript has a special implicit conversion for normal completions
when their actual values stored in the $\code{Value}$ field are necessary.
An actual value is necessary in various contexts such as
conditions, values of field updates, and operands of operators.
For example, if the variable $\x$ has a normal completion with
\code{42} as its actual value, $\code{x + 1}$ should be \code{43} because the
normal completion gets implicitly converted into its actual value \code{42}.
We define a unary operator $\escaped$ to explicitly represent this conversion:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{\columnwidth}{!}{$
    \escaped \val = \left\{
      \begin{array}{ll}
        \val &
        \text{if} \; \val \; \text{is not a completion}\\

@@

        \text{unchecked abrupt completion} \; \val &
        \text{otherwise}\\
      \end{array}
    \right.
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
The operand checker detects unchecked abrupt completion bugs by assuming
that the operator $\escaped$ is used when the actual value is necessary.

### 2021-04-22 paper/ase21/conclusion.tex
Reflected comments

\section{Conclusion}\label{sec:conclusion}
Checking the correctness of ECMAScript is essential because an incorrect description
in ECMAScript can lead to wrong implementations of JavaScript engines. However,
since ECMAScript is annually released and developed in an open process, checking
its correctness becomes more labor-intensive and error-prone.  To alleviate the problem,
we propose $\tool$, a JavaScript Specification Type Analyzer using Refinement.
It is the first tool that performs \textit{type analysis} on JavaScript specifications and
detects specification bugs using a \textit{bug detector}.  We also present
\textit{condition-based refinement} for type analysis, which prunes out infeasible abstract states
using conditions of assertions and branches to improve the analysis precision.
We evaluated $\tool$ with all 864 versions in the official ECMAScript repository
for the last three years from 2018 to 2021.  It took \inred{137.3} seconds on average
to perform type analysis for each version, and detected \inred{157} type-related specification bugs with
\inred{59.2}\% precision; \inred{93} out of \inred{157} reported bugs are true bugs.
Among them, \inred{14} bugs are newly detected by $\tool$, and the
committee confirmed them all.

>>>>

\section{Conclusion}\label{sec:conclusion}
Checking the correctness of ECMAScript is essential because an incorrect description
in ECMAScript can lead to wrong implementations of JavaScript engines. However,
since ECMAScript is annually released and developed in an open process, checking
its correctness becomes more labor-intensive and error-prone.  To alleviate the problem,
we propose $\tool$, a JavaScript Specification Type Analyzer using Refinement.
It is the first tool that performs \textit{type analysis} on JavaScript specifications and
detects specification bugs using a \textit{bug detector}.  We also present
\textit{condition-based refinement} for type analysis, which prunes out infeasible abstract states
using conditions of assertions and branches to improve the analysis precision.
We evaluated $\tool$ with all 864 versions in the official ECMAScript repository
for the last three years from 2018 to 2021.  It took 137.3 seconds on average
to perform type analysis for each version, and detected 157 type-related specification bugs with
59.2\% precision; 93 out of 157 reported bugs are true bugs.
Among them, 14 bugs are newly detected by $\tool$, and the
committee confirmed them all.

### 2021-04-22 paper/ase21/eval.tex
Reflected comments

Figure~\ref{fig:stat} shows the statistics of the type analysis using $\tool$ for
864 versions of ECMAScript: (a) the number of analyzed functions, (b) the number
of flow- and type-sensitive views, (c) the number of worklist iterations, and
(d) the analysis time.  For each version, $\tool$ analyzed
\inred{1,696.6} functions on average.  Since ECMAScript has gradually evolved,
it analyzed \inred{1,491} functions for the first version in 2018
but analyzed \inred{1,864} functions in the latest.
$\tool$ analyzes functions with flow- and type-sensitive views.
On average, each version has \inred{92.0}K views and each function has
\inred{54.1}~views.

We measured the performance of $\tool$ with the worklist iteration number
and the analysis time.  For each version of ECMAScript,
$\tool$ took \inred{137.3} seconds with \inred{301.6}K iterations of
the worklist algorithm on average.  The average analysis time consists of \inred{8.0} seconds
for the specification extraction (\stextsf{extract}),
\inred{128.5} seconds for the type analysis (\stextsf{analyze}), and
\inred{0.8} seconds for the bug detection (\stextsf{detect}).
Therefore, We believe that $\tool$ is enough to be as part of continuous
integration pipeline in open development process of ECMAScript.

@@

We measured the analysis precision with the number of true bugs in
the type-related specification bugs detected by $\tool$.
As summarized in the \stextsf{refine} column of Table~\ref{table:precision}, the analysis precision
is \inred{59.2}\%; \inred{93} out of \inred{157} detected bugs are true bugs.
The reference checker detected the most bugs with \inred{80.8}\% precision;
\inred{17} unknown variables (\stextsf{UnknownVar}) and
\inred{46} duplicated variable declarations (\stextsf{DuplicatedVar}) are true bugs.
We found \inred{four} missing parameters (\stextsf{MissingParam}) with \inred{100.0}\% precision and
\inred{four} assertion failures (\stextsf{Assertion}) with \inred{12.9}\% precision.
Finally, the operand checker detected
\inred{two} non-numeric operand bugs (\stextsf{NoNumber}) with \inred{33.3}\% precision and
\inred{20} unchecked abrupt completion bugs (\stextsf{Abrupt}) with \inred{52.6}\% precision.

To understand the impact of the detected true bugs, we extended $\tool$ to
automatically extract when they are created and resolved in the ECMAScript
official repository.  A bug is \textit{created} when it exists
in a specific version but does not exist in its previous version, and
a bug is \textit{resolved} vice versa. The \textit{life span} of a bug denotes
the number of days between the created date and the resolved date.
Figure~\ref{fig:life} illustrates the life spans of true bugs;
Figure~\ref{fig:life}(a) depicts the life spans sorted by creation and
Figure~\ref{fig:life}(b) depicts the histogram of the life spans in a logarithmic scale.
Among \inred{93} true bugs, \inred{48} bugs are \textit{inherited},
which means that they are created before 2018,
and \inred{14} bugs still exist in the latest ECMAScript, which are newly detected by $\tool$.
We discuss the details of \inred{14} newly found bugs in Section~\ref{sec:new-bug}.
Even though we assume that \inred{48} inherited bugs are created on January 1, 2018,
the average life spans is \inred{414.5} and the maximum life span is \inred{1,164}.
All the bugs with the maximum life span are inherited ones and they are all newly detected.

We manually investigated \inred{64} false-positive bugs to understand why
$\tool$ detected them.  Among them, \inred{17} bugs are due to extraction failure
of mechanized specifications caused by wrong writing styles.
Because ECMAScript is written in HTML, $\jiset$ extracts abstract algorithms
using the \code{emu-alg} HTML tag.  Unfortunately, several abstract algorithms are
defined with the opening tag \code{<emu-alg>} but without the closing tag \code{</emu-alg>},
which causes extraction failure of mechanized specifications leading
to false-positive bugs.  The remaining \inred{47} bugs are due to imprecise analysis.
We found that \inred{28} bugs are due to imprecise analysis of the
conditions of assertions and branches for specific function calls.
For example, consider the following algorithm step for \textbf{GetValue}:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \includegraphics[width=0.7\columnwidth]{img/adv-refine-example}
  \vspace*{-0.5em}
\end{figure} \noindent
Since \textbf{IsPropertyReference} always returns
$\code{false}$ when the $\code{Base}$ field of a given reference record is
$\nconst{unresolvable}$, the field access $V$.[[Base]] cannot be
$\nconst{unresolvable}$ on line 4.a.  However, because the type analysis
does not compute such information,
$\nconst{unresolvable}$ is also passed as the argument of \textbf{ToObject}.
We believe that an advanced refinement technique can
resolve this problem by pruning out infeasible field types depending on specific contexts.

@@

    ES12-8 &
    Arguments &
    2 &
    \makecell[l]{
        Abrupt completions are used in \textbf{DefineOwnProperty} and
        \textbf{GetOwnProperty} \\ for \jscode{arguments} objects without any
        checks.
    } &
    \stextsf{\footnotesize Operand} &
    \inred{2015-12-16} &
    \inred{1,910 days}\\
  \end{tabular}
  }
  \vspace*{-1.5em}
\end{table*}

@@

For performance comparison, Figure~\ref{fig:performance-compare} presents the
iterations and analysis time without and with refinement.
Figures~\ref{fig:performance-compare}(a) and
\ref{fig:performance-compare}(c) are histograms of the iterations and analysis
time, respectively, and Figures~\ref{fig:performance-compare}(b) and
\ref{fig:performance-compare}(d) are scatter charts for their ratios.
Without refinement, the type analysis took \inred{91.9} seconds with \inred{261.5}K
iterations on average.  After applying refinement, the number of iterations is increased
at least \inred{0.99}x, at most \inred{1.36}x, and \inred{1.16}x on average, and
the analysis time is increased at least \inred{1.05}x, at most \inred{1.99}x,
and \inred{1.41}x on average.

Table~\ref{table:precision} shows the analysis precision without refinement,
with refinement, and their difference.  The refinement improved the analysis
precision from \inred{33.0}\% to \inred{59.2}\% by removing \inred{122}
false-positive bugs and detecting \inred{one} more true bug.  Among six
bug kinds, the most significant improvement is for non-numeric
operand bugs (\stextsf{NoNumber}) from \inred{3.1}\% to \inred{33.3}\%
by removing \inred{59} false-positive bugs.  The refinement technique
successfully prunes out non-numeric values for numeric types.
The refinement significantly increased the analysis precision also for unknown
variable bugs (\stextsf{UnknownVar}) and assertion failures
(\stextsf{Assertion}) by removing \inred{29} and \inred{25} false-positive bugs, respectively.
Because $\tool$ can precisely analyze callees of function invocations
without refinement, we found no improvement for missing
parameter bugs (\stextsf{MissingParam}).

@@

Among \inred{93} true bugs detected by $\tool$, \inred{14} are newly
detected and still exist in the latest version of ECMAScript.
Table~\ref{table:new-bug} summarizes the bugs, their
related JavaScript language features, and their life spans.
Except for two bugs in ES12-8, all bugs were introduced in the initial
commit of the open development on September 22, 2015.
Thus, 12 newly detected bugs last for 1,996 days until March 9, 2021.
The two bugs in ES12-8 were created when a contributor introduced
the prefixes \textbf{?} and \textbf{!} on December 16, 2015, and they last for 1,910 days.
We reported the newly detected bugs to TC39, and all of them were
confirmed by the committee and will be fixed in ECMAScript 2022 (ES13).

>>>>

Figure~\ref{fig:stat} shows the statistics of the type analysis using $\tool$ for
864 versions of ECMAScript: (a) the number of analyzed functions, (b) the number
of flow- and type-sensitive views, (c) the number of worklist iterations, and
(d) the analysis time.  For each version, $\tool$ analyzed
1,696.6 functions on average.  Since ECMAScript has gradually evolved,
it analyzed 1,491 functions for the first version in 2018
but analyzed 1,864 functions in the latest.
$\tool$ analyzes functions with flow- and type-sensitive views.
On average, each version has 92.0K views and each function has
54.1~views.

We measured the performance of $\tool$ with the worklist iteration number
and the analysis time.  For each version of ECMAScript,
$\tool$ took 137.3 seconds with 301.6K worklist iterations
on average.  The average analysis time is 8.0 seconds
for specification extraction (\stextsf{extract}),
128.5 seconds for type analysis (\stextsf{analyze}), and
0.8 seconds for bug detection (\stextsf{detect}).
The performance overhead is modest enough for $\tool$ to be integrated
in the open development process of ECMAScript.

@@

We measured the analysis precision with the ratio of true bugs in the reported bugs by $\tool$.
As summarized in the \stextsf{refine} column of Table~\ref{table:precision}, the analysis precision
is 59.2\%; 93 out of 157 detected bugs are true bugs.
The reference checker detected the most bugs with 80.8\% precision;
17 unknown variables (\stextsf{UnknownVar}) and
46 duplicated variable declarations (\stextsf{DuplicatedVar}) are true bugs.
We found four missing parameters (\stextsf{MissingParam}) with 100.0\% precision and
four assertion failures (\stextsf{Assertion}) with 12.9\% precision.
Finally, the operand checker detected
two non-numeric operand bugs (\stextsf{NoNumber}) with 33.3\% precision and
20 unchecked abrupt completion bugs (\stextsf{Abrupt}) with 52.6\% precision.

To understand the impact of the detected true bugs, we extended $\tool$ to
automatically extract when they are created and resolved in the ECMAScript
official repository.  A bug is \textit{created} when it exists
in a specific version but does not exist in its previous version, and
a bug is \textit{resolved} vice versa. The \textit{life span} of a bug denotes
the number of days between the created date and the resolved date.
Figure~\ref{fig:life} illustrates the life spans of true bugs;
Figure~\ref{fig:life}(a) depicts the life spans sorted by creation and
Figure~\ref{fig:life}(b) depicts the histogram of the life spans in a logarithmic scale.
Among 93 true bugs, 48 bugs are \textit{inherited},
which means that they are created before 2018,
and 14 bugs still exist in the latest ECMAScript, which are newly detected by $\tool$.
We discuss the details of 14 newly found bugs in Section~\ref{sec:new-bug}.
Even though we assume that 48 inherited bugs are created on January 1, 2018,
the average life span is 414.5 and the maximum life span is 1,164.
All the bugs with the maximum life span are inherited ones and they are all newly detected.

We manually investigated 64 false-positive bugs to understand why
$\tool$ detected them.  Among them, 17 bugs are due to extraction failure
of mechanized specifications caused by wrong writing styles.
Because ECMAScript is written in HTML, $\jiset$ extracts abstract algorithms
using the \code{emu-alg} HTML tag.  Unfortunately, several abstract algorithms are
defined with the opening tag \code{<emu-alg>} but without the closing tag \code{</emu-alg>},
which causes extraction failure of mechanized specifications leading
to false-positive bugs.  The remaining 47 bugs are due to imprecise analysis.
We found that 28 bugs are due to imprecise analysis of the
conditions of assertions and branches for specific function calls.
For example, consider the following algorithm step for \textbf{GetValue}:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \includegraphics[width=0.7\columnwidth]{img/adv-refine-example}
  \vspace*{-0.5em}
\end{figure} \noindent
Since \textbf{IsPropertyReference} always returns
$\code{false}$ when the $\code{Base}$ field of a given reference record is
$\nconst{unresolvable}$, the field access $V$.[[Base]] cannot be
$\nconst{unresolvable}$ on line 4.a.  However, because the type analysis
does not compute such information,
$\nconst{unresolvable}$ is also passed as the argument of \textbf{ToObject}.
We believe that an advanced refinement technique can
resolve this problem by pruning out infeasible field types depending on specific contexts.

@@

    ES12-8 &
    Arguments &
    2 &
    \makecell[l]{
        Abrupt completions are used in \textbf{DefineOwnProperty} and
        \textbf{GetOwnProperty} \\ for \jscode{arguments} objects without any
        checks.
    } &
    \stextsf{\footnotesize Operand} &
    2015-12-16 &
    1,910 days\\
  \end{tabular}
  }
  \vspace*{-1.5em}
\end{table*}

@@

For performance comparison, Figure~\ref{fig:performance-compare} presents the
iterations and analysis time without and with refinement.
Figures~\ref{fig:performance-compare}(a) and
\ref{fig:performance-compare}(c) are histograms of the iterations and analysis
time, respectively, and Figures~\ref{fig:performance-compare}(b) and
\ref{fig:performance-compare}(d) are scatter charts for their ratios.
Without refinement, the type analysis took 91.9 seconds with 261.5K
iterations on average.  After applying refinement, the number of iterations is increased
at least 0.99x, at most 1.36x, and 1.16x on average, and
the analysis time is increased at least 1.05x, at most 1.99x,
and 1.41x on average.

Table~\ref{table:precision} shows the analysis precision without refinement,
with refinement, and their difference.  The refinement improved the analysis
precision from 33.0\% to 59.2\% by removing 122
false-positive bugs and detecting one more true bug.  Among six
bug kinds, the most significant improvement is for non-numeric
operand bugs (\stextsf{NoNumber}) from 3.1\% to 33.3\%
by removing 59 false-positive bugs.  The refinement technique
successfully prunes out non-numeric values for numeric types.
The refinement significantly increased the analysis precision also for unknown
variable bugs (\stextsf{UnknownVar}) and assertion failures
(\stextsf{Assertion}) by removing 29 and 25 false-positive bugs, respectively.
Because $\tool$ can precisely analyze callees of function invocations
without refinement, we found no improvement for missing
parameter bugs (\stextsf{MissingParam}).

@@

Among 93 true bugs detected by $\tool$, 14 are newly
detected and still exist in the latest version of ECMAScript.
Table~\ref{table:new-bug} summarizes the bugs, their
related JavaScript language features, and their life spans.
Except for two bugs in ES12-8, all bugs were introduced in the initial
commit of the open development on September 22, 2015.
Thus, 12 newly detected bugs last for 1,996 days until March 9, 2021.
The two bugs in ES12-8 were created when a contributor introduced
the prefixes \textbf{?} and \textbf{!} on December 16, 2015, and they last for 1,910 days.
We reported the newly detected bugs to TC39, and all of them were
confirmed by the committee and will be fixed in ECMAScript 2022 (ES13).

### 2021-04-22 paper/ase21/intro.tex
Reflected comments

The correctness of ECMAScript is critical because an incorrect
description in the specification can lead to wrong
implementations of JavaScript engines in various fields.  However,
all the specification updates are currently manually reviewed by the Ecma
Technical Committee 39 (TC39) without any automated tools.
Such a manual review process is inherently labor-intensive and error-prone,
making ECMAScript vulnerable to specification bugs.
Besides, in late 2014, the committee announced the yearly release cadence and open development
process of ECMAScript to quickly adapt to evolving development environments.
According to Park et al.~\cite{jiset}, the average number of updated steps of abstract
algorithms between consecutive releases from ECMAScript 2016 (ES7) to 2019 (ES10) is 9645.5.
In the official ECMAScript repository, \inred{1,355} pull
requests and \inred{2,005} commits exist in the master branch.
Therefore, manually checking all the frequent specification updates is
a challenging task.

@@

To alleviate this problem, we propose a novel tool $\tool$, a \textbf{J}avaScript
\textbf{S}pecification \textbf{T}ype \textbf{A}nalyzer using
\textbf{R}efinement. In order to perform a \textit{type analysis} on ECMAScript
to statically detect type-related specification bugs automatically,
the main challenge is that ECMAScript describes abstract algorithms in
a natural language, English. While researchers~\cite{lambdajs, jscert, kjs}
have formally defined various JavaScript semantics for different
versions of ECMAScript by hand, manual formalization is not suitable for
automatically detecting bugs in rapidly evolving JavaScript specifications. 
Thus, recent approaches in diverse fields such as system architectures~\cite{x86, arm},
network protocols~\cite{basespec}, and language specifications~\cite{spectest, javadoc}
have utilized information directly extracted from specifications written in a natural language
to lessen such burdens.
Among them, $\jiset$~\cite{jiset} compiles ECMAScript abstract algorithms written in
a structured natural language to functions in $\ires$, an untyped
intermediate representation for ECMAScript.
Therefore, $\tool$ leverages $\jiset$ to mechanically handle JavaScript specifications.

For mechanized JavaScript specifications by $\jiset$, $\tool$ performs
a type analysis of compiled functions using \textit{specification types}
defined in ECMAScript. ECMAScript contains not only JavaScript
language types but also specification types such as abstract syntax
trees (ASTs), internal list-like structures, and internal records
including environments, completions, and property descriptors. We
define their type hierarchies based on subtype relations and fields for record and AST types.
Using such type information, $\tool$ performs a type analysis and detects specification bugs using
a \textit{bug detector} consisting of four checkers: 1) a reference
checker, 2) an arity checker, 3) an assertion checker, and 4) an operand checker.
$\tool$ also uses a \textit{condition-based refinement} for type
analysis, which prunes out infeasible parts in abstract states by using conditions
of assertions and branches to improve the precision of type analysis.
We evaluated $\tool$ with all \inred{864} versions in the official
ECMAScript repository for the recent three years from 2018 to 2021.
The experiments showed that the refinement technique could reduce the number of
false-positive bugs caused by spurious types inferred by imprecise type analysis.

The main contributions of this paper are as follows:
\begin{itemize}
  \item We present $\tool$, the first tool that performs a \textit{type
    analysis} on ECMAScript written in a natural language to check the correctness of JavaScript language
    specifications.  $\tool$ automatically detects type-related specification
    bugs such as unknown variables, duplicated variables, missing
    parameters, assertion failures, ill-typed operands, and unchecked
    abrupt completion bugs.
  \item We present a \textit{condition-based refinement} for type analysis of
    ECMAScript to reduce the number of false-positive bugs by enhancing the analysis
    precision.  We show that the refinement technique increases the analysis
    precision from \inred{33.0}\% to \inred{59.2}\% by removing \inred{122}
    false bugs and detecting \inred{one} more true bug.
  \item We demonstrate the practicality of $\tool$. It takes \inred{137.3}
    seconds on average to perform a type analysis for each version of ECMAScript and detected
    \inred{157} type-related specification bugs with \inred{59.2}\% precision;
    \inred{93} out of \inred{157} bugs are true bugs.  Among them, $\tool$
    newly detected \inred{14} bugs, and the ECMAScript committee confirmed them all.
\end{itemize}

>>>>

The correctness of ECMAScript is critical because an incorrect
description in the specification can lead to wrong
implementations of JavaScript engines in various fields.  However,
all the specification updates are currently manually reviewed by the Ecma
Technical Committee 39 (TC39) without any automated tools.
Such a manual review process is inherently labor-intensive and error-prone,
making ECMAScript vulnerable to specification bugs.
Besides, in late 2014, the committee announced the yearly release cadence and open development
process of ECMAScript to quickly adapt to evolving development environments.
According to Park et al.~\cite{jiset}, the average number of updated steps of abstract
algorithms between consecutive releases from ECMAScript 2016 (ES7) to 2019 (ES10) is 9645.5.
In the official ECMAScript repository, 1,355 pull
requests and 2,005 commits exist in the master branch.
Therefore, manually checking all the frequent specification updates is
a challenging task.

@@

To alleviate this problem, we propose a novel tool $\tool$, a \textbf{J}avaScript
\textbf{S}pecification \textbf{T}ype \textbf{A}nalyzer using
\textbf{R}efinement. The main challenge of ECMAScript type analysis to
statically detect type-related specification bugs automatically is
that ECMAScript describes abstract algorithms in a natural language,
English.  While researchers~\cite{lambdajs, jscert, kjs}
have formally defined various JavaScript semantics for different
versions of ECMAScript by hand, manual formalization is not suitable for
automatically detecting bugs in rapidly evolving JavaScript specifications. 
Thus, recent approaches in diverse fields such as system architectures~\cite{x86, arm},
network protocols~\cite{basespec}, and language specifications~\cite{spectest, javadoc}
have utilized information directly extracted from specifications written in a natural language
to lessen such burdens.
Among them, $\jiset$~\cite{jiset} compiles ECMAScript abstract algorithms written in
a structured natural language to functions in $\ires$, an untyped
intermediate representation for ECMAScript.
Therefore, $\tool$ leverages $\jiset$ to mechanically handle JavaScript specifications.

$\tool$ takes mechanized JavaScript specifications from $\jiset$ and performs
a type analysis of compiled functions using \textit{specification types}
defined in ECMAScript.  ECMAScript contains not only JavaScript
language types but also specification types such as abstract syntax
trees (ASTs), internal list-like structures, and internal records
including environments, completions, and property descriptors.
\inred{We define their type hierarchies based on subtype relations and fields for record and AST types.}
Using such type information, $\tool$ performs a type analysis and detects specification bugs using
a \textit{bug detector} consisting of four checkers: 1) a reference
checker, 2) an arity checker, 3) an assertion checker, and 4) an operand checker.
$\tool$ also uses a \textit{condition-based refinement} for type
analysis, which prunes out infeasible parts in abstract states by using conditions
of assertions and branches to improve the precision of type analysis.
We evaluated $\tool$ with all 864 versions in the official
ECMAScript repository for the recent three years from 2018 to 2021.
The experiments showed that the refinement technique could reduce the number of
false-positive bugs caused by spurious types inferred by imprecise type analysis.

The main contributions of this paper are as follows:
\begin{itemize}
  \item We present $\tool$, the first tool that performs a \textit{type
    analysis} on ECMAScript written in a natural language to check the correctness of JavaScript language
    specifications.  $\tool$ automatically detects type-related specification
    bugs such as unknown variables, duplicated variables, missing
    parameters, assertion failures, ill-typed operands, and unchecked
    abrupt completion bugs.
  \item We present a \textit{condition-based refinement} for type analysis of
    ECMAScript to reduce the number of false-positive bugs by enhancing the analysis
    precision.  We show that the refinement technique increases the analysis
    precision from 33.0\% to 59.2\% by removing 122
    false bugs and detecting one more true bug.
  \item We demonstrate the practicality of $\tool$. It takes 137.3
    seconds on average to perform a type analysis for each version of ECMAScript and detected
    157 type-related specification bugs with 59.2\% precision;
    93 out of 157 bugs are true bugs.  Among them, $\tool$
    newly detected 14 bugs, and the ECMAScript committee confirmed them all.
\end{itemize}
